Misc Slides

### 2016-10-02 inst/examples/manuscript-krakow.Rmd
ok

  res <- titlecount_timeline(dfs, "gatherings", nmin = 15, mode = "n") 
  print(res$plot + ggtitle(paste(catal, " (n)", sep = "")))

  res <- titlecount_timeline(dfs, "gatherings", nmin = 15, mode = "percentage") 
  print(res$plot + ggtitle(paste(catal, " (%)", sep = "")))
}
```

>>>>

  res <- timeline(dfs, field = "gatherings", nmin = 15, mode = "absolute") 
  print(res$plot + ggtitle(paste(catal, " (n)", sep = "")))

  res <- timeline(dfs, field = "gatherings", nmin = 15, mode = "percentage") 
  print(res$plot + ggtitle(paste(catal, " (%)", sep = "")))
}
```

### 2016-10-02 inst/examples/slides.Rmd
ok

```{r, fig.width=15, fig.height=5, message=FALSE, warning=FALSE}
library(bibliographica)
titlecount_timeline(subset(df0, catalog == "Fennica"), 
          "publisher", nmin = 500, mode = "n")$plot
```

>>>>

```{r, fig.width=15, fig.height=5, message=FALSE, warning=FALSE}
library(bibliographica)
timeline(subset(df0, catalog == "Fennica"), 
          group = "publisher", nmin = 500, mode = "absolute")$plot
```
